Dynamical Properties of Molecular Cloud Complexes in a Redshift 6 Prototypical Galaxy at the Epoch of Reionization

### 2018-09-10 WRITEUP/ms.tex
added ref

% a bit on caveat
One should, however, keep in mind that 
the slope of the CMF reported here is subject
to the uncertainties in the analysis method and the resolution of our simulation. 
That is, we are likely biased to finding more massive clouds due to resolution effects; 
it is possible that we may identify more and less massive MCs if our simulation 
was done at a higher resolution. 
That said, one must acknowledge that such a zoom-in simulation is currently too expensive to perform with 
existing computational power.
In any case, similarly massive molecular clouds have been reported in simulations done at higher resolution (i.e., 
in closed box simulations; \citealt{}). 
{\DL I'm forgetting the paper I want to cite..}
It is therefore conceivable that our results are not that far off in spite of the limited resolution ($l\approx$30\,pc).
Future higher resolution zoom-in simulations would certainly be useful to understand
the evolving dynamical properties of the lower-mass molecular structures in
galaxies at EoR under the influence of gas inflow/outflow (i.e., accounting for energy injection at large scale due to infall/outflow).
% 
%On the contrary, an advantage of using cosmological zoom-in simulations for this study
%is that our computational boxes are not closed, allowing us to examine how
%the molecular complexes' properties vary under the influence of gas inflow/outflow 
%(see e.g., \citealt{Klessen10a, Goldbaum11a}). % turbulence when disk still accreting gas

>>>>

% a bit on caveat
One should, however, keep in mind that 
the slope of the CMF reported here is subject
to the uncertainties in the analysis method and the resolution of our simulation. 
That is, we are likely biased to finding more massive clouds due to resolution effects; 
it is possible that we may identify more and less massive MCs if our simulation 
was done at a higher resolution. 
That said, one must acknowledge that such a zoom-in simulation is currently too expensive to perform with 
existing computational power.
In any case, similarly massive molecular clouds have been reported in simulations done at higher resolution (i.e., 
in closed box simulations; \citealt{Behrendt16a}). 
It is therefore conceivable that our results are not that far off in spite of the limited resolution ($l\approx$30\,pc).
Future higher resolution zoom-in simulations would certainly be useful to understand
the evolving dynamical properties of the lower-mass molecular structures in
galaxies at EoR under the influence of gas inflow/outflow (i.e., accounting for energy injection at large scale due to infall/outflow).
% 
%On the contrary, an advantage of using cosmological zoom-in simulations for this study
%is that our computational boxes are not closed, allowing us to examine how
%the molecular complexes' properties vary under the influence of gas inflow/outflow 
%(see e.g., \citealt{Klessen10a, Goldbaum11a}). % turbulence when disk still accreting gas
